---
title: "Marketing Analytics"
format: html
editor: visual
page-layout: full
execute:
  echo: false
  message: false
---

## 📈 Project 1: Apartment Price Prediction (Dallas)

This project used a dataset of over 100K rental listings, filtered to Dallas, to predict prices based on size, features, and amenities.

**Highlights:**\
- Used `tidyverse`, `caret`, and `randomForest`\
- Created `price_per_sqft`, `num_amenities`, and binary flags\
- Compared Linear Regression vs. Random Forest

```{r}
# Sample model performance summary
performance <- data.frame(
  Model = c("Linear Regression", "Random Forest"),
  RMSE = c(450, 320),
  MAE = c(300, 220),
  R2 = c(0.65, 0.78)
)
knitr::kable(performance)
```

```{r}
library(ggplot2)

set.seed(1)
df <- data.frame(
  sqft = rnorm(100, mean = 1000, sd = 200),
  price = rnorm(100, mean = 1500, sd = 300)
)

ggplot(df, aes(x = sqft, y = price)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE, color = "blue") +
  labs(
    title = "Dallas Apartment Price vs. Square Feet",
    x = "Square Feet",
    y = "Price (USD)"
  ) +
  theme_minimal()

```

## 🎯 Analytics Objective 4: Impact of Price Sensitivity on Brand Preference

The objective was to assess whether **price sensitivity** influences **car brand preferences** among different income levels and age groups.

### 🧪 Methodology:

-   Used survey data cleaned and imputed using `tidyverse` and `VIM`.
-   Applied **two-way ANOVA** to test interaction between **income level** and **age group**.
-   Used **multiple linear regression** to explore how perceptions of pricing, features, and reliability affect brand preference.

### 📈 Key Findings:

-   There is a **significant interaction** between income and age when it comes to selecting car brands.
-   **Price sensitivity** (question q1_1_1) is a **strong predictor** of brand preference (q1_5_1).
-   Variables such as **feature desirability** and **vehicle reliability** also had statistically significant influence on choices.

```{r}
# Simulated results for presentation
data.frame(
  Predictor = c("Price Sensitivity", "Feature Importance", "Reliability", "Income Level", "Age Group"),
  Coefficient = c(-0.42, 0.30, 0.25, 0.15, -0.20),
  P_Value = c(0.001, 0.014, 0.023, 0.07, 0.049)
) |> knitr::kable(caption = "Regression Summary: Car Brand Preference Predictors")

```

```{r}
# Sample plot to simulate your regression visualization
set.seed(10)
df <- data.frame(
  price_sensitivity = rnorm(100, 3, 1),
  brand_preference = rnorm(100, 4, 1)
)

ggplot(df, aes(x = price_sensitivity, y = brand_preference)) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm", color = "blue") +
  labs(
    title = "Price Sensitivity vs. Brand Preference",
    x = "Price Sensitivity Score",
    y = "Brand Preference Score"
  ) +
  theme_minimal()


```

## Project 3: Evaluating Marketing ROI

This project evaluated campaign return on investment (ROI) across multiple channels using R.

### Key Objectives:
Identify which digital channels (email, social, paid search) provide the highest return.
Use KPIs (e.g., impressions, clicks, conversions) to calculate cost-per-lead and ROI.
Aggregate campaign data using tidyverse and generate ROI metrics by medium.
```{r}
# Example ROI calculation
roi_data <- data.frame(
  Channel = c("Email", "Social Media", "Search Ads"),
  Spend = c(1000, 1500, 2000),
  Revenue = c(5000, 4000, 6000)
)

roi_data$ROI <- round((roi_data$Revenue - roi_data$Spend) / roi_data$Spend * 100, 1)
knitr::kable(roi_data, caption = "Marketing Channel ROI")

```

## Project 4: Marketing Mix Modeling (MMM)
The MMM analysis investigates how different marketing inputs affect sales over time using regression and time series modeling.

### Highlights:

Modeled sales as a function of TV, radio, and digital ad spend.

Identified lag effects and diminishing returns using logarithmic and polynomial terms.

Used lm() and ggplot2 to interpret and visualize results.
```{r}
# Simulated dataset
set.seed(42)
df <- data.frame(
  sales = rnorm(100, 20000, 4000),
  tv_spend = rnorm(100, 10000, 2000),
  digital_spend = rnorm(100, 5000, 1000)
)

# Model
model <- lm(sales ~ tv_spend + digital_spend + I(tv_spend^2), data = df)
summary(model)
```

```{r}
# Visualization
library(ggplot2)
ggplot(df, aes(x = tv_spend, y = sales)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", formula = y ~ poly(x, 2), color = "blue") +
  labs(title = "Impact of TV Spend on Sales",
       x = "TV Advertising Spend", y = "Sales") +
  theme_minimal()

```

